Rapid technological progress in \\ white light-emitting diodes and its sources in innovation and technology spillovers

### 2022-08-06 2_SSL_EES/article/article_supplementary.tex
added figures to supplementary information

\title{Something something progress in light}

@@

@@

Note that a humorous illustration of this trend in this figure has been provided by Randall Munroe in \href{https://xkcd.com/1603/}{https://xkcd.com/1603/}.

>>>>

\title{Rapid technological progress in \\ white light-emitting diodes and its sources in innovation and technology spillovers}

@@

\section{Cost model sensitivity analysis}

\begin{figure}
	\centering
    \includegraphics[width=\textwidth]{2_SSL_EES/article/figures/costmodel_sensitivity.pdf}
	\caption{Panels a-b: Sensitivity analysis of selected cost model parameters. Note the decreasing sensitivity to cost model parameters as the number of die per wafer increases.}
	\label{fig:costmodel_calibration}
\end{figure}

Sensitivity analysis of selected cost model parameters. Note the decreasing sensitivity to cost model parameters as the number of die per wafer increases.

A preliminary sensitivity analysis (panels a-b of Figure XX) confirms these preliminary findings, showing the largest deviation for changes in these parameters.

\section{Cost model comparison with reported industry data}

\begin{figure}
	\centering
    \includegraphics[width=\textwidth]{2_SSL_EES/article/figures/costmodel_calibration.pdf}
	\caption{Modelled manufacturing cost for light-emitting diode packages split by manufacturing step category. The top graph shows the data from LEDCOM model and round table discussions published by the United States Department of Energy (DoE). The bottom graph shows the results of the cost model developed in this thesis. Hatched bars are projections given by the sources. Inset plot shows the number of die per wafer (DPW) calculated for different wafer sizes used in the model.}
	\label{fig:costmodel_calibration}
\end{figure}

We note differences between our model and costs reported to the US Department of Energy (DoE) by industry. For instance, the share of the epitaxy step is larger in the DoE model. This can in part be explained by our model relying on state-of-the-art equipment, while industry might not run low-power and mid-power chip production on these, more expensive, reactors. The packaging part of the manufacturing process is increasing in importance, which has been confirmed by researchers and industry reports on wafer-level packaging.

@@

Note that a humorous illustration of the trend of dramatic improvements in luminous flux shown in this figure has been provided by cartoonist Randall Munroe in \href{https://xkcd.com/1603/}{https://xkcd.com/1603/}.
